%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Build and Release Engineer} % Job title
    {General Electric - Healthcare} % Organization
    {Seattle, WA} % Location
    {March 2019 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built data pipeline for AWS Billing data for hundreds of AWS Accounts using AWS Glue, Athena, and QuickSight}
        \item {Assisted in migration of AI application deployed on-prem to an AWS EKS cluster using Terraform}
        \item {Added additional functionality to centralized log delivery pipeline using AWS Lambda, Kinesis, S3, and CloudWatch}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {DevOps Engineer} % Job title
    {The Walt Disney Company} % Organization
    {Seattle, WA} % Location
    {May 2018 - March 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Responsible for user management in AWS, creating and troubleshooting AWS infrastructure to include IAM resources, Linux EC2, S3, RedShift and other services.}
        \item {Advocated for and led the adoption of cloud infrastructure automation using Terraform, as well as Kubernetes for applications that fit into a microservice architecture.}
        \item {Assist in automating and deploying software through the CICD pipeline using GitLab, Ansible and Kubernetes.}
        \item {Assist in redesign and creation of new data platform using Apache Airflow.}
        \item {Advise on architecture and design of computer vision project using Kubernetes (AWS GPU Instance nodes), Apache Airflow and Snowflake.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {DevOps Engineer Intern} % Job title
    {CoalFire} % Organization
    {Seattle, WA} % Location
    {June 2016 - Aug 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked on an open source part of Microsoft Azure, fixing a security bug in the way that their virtual machines handle Linux drive partitions.}
        \item {Monitored and assisted in troubleshooting problems with large virtual network of Linux security appliances.}
        \item {Assisted in automation of AWS Linux and Windows infrastructure, and migration from physical to virtual systems.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {NOC Technician}% Job title
    {Optic Fusion} % Organization
    {Tacoma, WA} % Location
    {January 2015 - August 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Monitor and troubleshoot customer servers, and large data center network.}
        \item {Maintained, created and migrated customers from physical Linux and Windows servers to virtual servers.}
        \item {Assist fiber to the home customers with basic troubleshooting and connectivity issues.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Food Service Specialist} % Job title
    {U.S. Army} % Organization
    {Joint Base Lewis McChord, WA} % Location
    {Dec. 2011 - Feb. 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Team leader for 5-7 soldiers.}
        \item {Responsible for preparation and service of food, including inventory management and accountability for high dollar items.}
      \end{cvitems}
    }
